Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-09 ms.tex
spellimg

If prsent, thermal
instabilities may cause the CNM to undergo cyclic
oscillations of rapid cooling and high accretion rates, followed by
quiescent periods once gas has been consumed and/or AGN feedback
becomes effective.  Such cycles are seen in numerical simulations of
elliptical galaxies on large scales and long timescales
(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes observations
showing that a fraction of early-type galaxies in the local universe
have undergone recent ($< 1-2$ Gyr old) star formation episodes
(\citealt{Donas+07}).

>>>>

If present, thermal
instabilities may cause the CNM to undergo cyclic
oscillations of rapid cooling and high accretion rates, followed by
quiescent periods once gas has been consumed and/or AGN feedback
becomes effective.  Such cycles are seen in numerical simulations of
elliptical galaxies on large scales and long timescales
(\citealt{Ciotti+10}).  Evidence for such periodic outbursts includes observations
showing that a fraction of early-type galaxies in the local universe
have undergone recent ($< 1-2$ Gyr old) star formation episodes
(\citealt{Donas+07}).
